Incremental Forward Reasoning for White-Box~Proof~Search

### 2025-02-24 paper.tex
Clarify future work
fix number of benchmark

Benchmark code and data are available in our supplement~\cite{supplement}.
The results shown below were obtained on a MacBook Pro with an Apple~M2 Pro processor and \SI{32}{GB} of RAM, averaging over \textcolor{red}{N} (TODO) runs per benchmark.

@@

One obvious extension of our method would be to exploit redundancy not just between contexts of parent and child goals, but also between those of siblings or even unrelated goals.
The forward state supports this since for any two goals, we can adapt a goal's saved forward state to a similar goal.

>>>>

Benchmark code and data are available in our supplement~\cite{supplement}.
The results shown below were obtained on a MacBook Pro with an Apple~M2 Pro processor and \SI{32}{GB} of RAM, averaging over 20 runs per benchmark.

@@

One obvious extension of our method would be to exploit redundancy not just between contexts of parent and child goals, but also between those of siblings or even unrelated goals.
This would require no changes to the forward state data structure; we would only need to find pairs of goals that produce minimal diffs.
